%% TeXworks instructions:
% !TeX root = ./assignment.tex
% !TEX encoding = UTF-8 Unicode
% !TEX program = arara
% !TEX TS-program = arara
% !TeX spellcheck = en-US

% arara: pdflatex
% arara: pdflatex: { synctex: yes }

%% Generate a report.xmpdata file with title and authors for PDF/A-compliant format %%


\documentclass[
    a4paper,            % specifica il formato A4 (default: letter)
    10pt,               % specifica la dimensione del carattere a 10
    oneside,            % serve per impaginare per stampa solo fronte
    english]
    {article}

\usepackage[T1]{fontenc}        % serve per impostare la codifica di output del font
\usepackage{textcomp}           % serve per fornire supporto ai Text Companion fonts
\usepackage[utf8]{inputenc}     % serve per impostare la codifica di input del font
\usepackage[english]{babel}
\usepackage{lmodern}            % carica una variante Latin Modern prodotto dal GUST

\usepackage[%
    strict,             % rende tutti gli warning degli errori
    autostyle,          % imposta lo stile in base al linguaggio specificato in babel
    english=american    % imposta lo stile per l'inglese
]{csquotes}                     % serve a impostare lo stile delle virgolette

\usepackage[%
    depth=3,            % equivale a bookmarksdepth di hyperref
    open=false,         % equivale a bookmarksopen di hyperref
    numbered=true       % equivale a bookmarksnumbered di hyperref
]{bookmark}                     % Gestisce i segnalibri meglio di hyperref
\usepackage{hyperref}           % Gestisce tutte le cose ipertestuali del pdf
\hypersetup{%
    pdfpagemode={UseNone},
    hidelinks,          % nasconde i collegamenti (non vengono quadrettati)
    hypertexnames=false,
    linktoc=all,        % inserisce i link nell'indice
    unicode=true,       % only Latin characters in Acrobat’s bookmarks
    pdftoolbar=false,   % show Acrobat’s toolbar?
    pdfmenubar=false,   % show Acrobat’s menu?
    plainpages=false,
    breaklinks,
    pdfstartview={Fit},
    pdfauthor={Niccolò Maltoni},
    pdfcreator={Niccolò Maltoni},
    pdftitle={Assignment 03 Prolog Report},
    pdflang={it}
}
\usepackage[%
    english,            % definizione delle lingue da usare
    nameinlink          % inserisce i link nei riferimenti
]{cleveref}                     % permette di usare riferimenti migliori dei \ref e dei varioref

% MARGINI LARGHI
\textwidth 6.3 in % Width of text line.
    \textheight 9.2 in
    \oddsidemargin 0 in      %   Left margin on odd-numbered pages.
    \evensidemargin 0 in      %   Left margin on even-numbered pages.
    \topmargin 0.2 in
    \headheight 0 in       %   Width of marginal notes.
    \headsep 0 in
    \topskip 0 in
    
\title{\vspace{-70pt}Assignment 03 -- ``Prolog''\footnote{Produce a documentation according to this template. Try to keep this document in one page, overall work no more than 6-7 hours, do the job yourself, deliver before the exam, consider the possibility of doing it this very week. Erase this and all other footnotes at the end before submitting.}}
\author{Riccardo Soro, matr: 851004, email: {\url{riccardo.soro@studio.unibo.it}}\\ repo: \url{https://github.com/riccardosoro/pps2017-asg03-prolog.git}}
\date{22/01/2019}


\begin{document}

\maketitle
\vspace{-30pt}

\subsection*{Description of the code you provide}
 \begin{itemize}
            \item
                Full solution to lab 10 along with final exercises: \texttt{inv}, \texttt{double}, \texttt{times}, \texttt{proj}.
                \begin{itemize}
                    \item Necessary time: $\sim$~4 hours
                \end{itemize}

            \item
                Full solution to lab 11, without Tic Tac Toe.
                \begin{itemize}
                                       \item Necessary time: $\sim$~4 hours
                \end{itemize}
        \end{itemize}

\subsection*{Techniques used}

\begin{itemize}
 \item Prolog search-space abilities
 \item Prolog use of unification and variables
 \item \ldots
\end{itemize}

\subsection*{Self-evaluation}

I found this experience very educational.
Surely 8 hours are not enough to master the language, but it has provided me with a useful basis for the future.
I liked the prolog because, unlike the languages we are used to, it is more intuitive in some respects (recursive problems).
In other respects, however, I continue to prefer other languages with which I am more confident.
 
\end{document}
    
    
